### 2015-08-12 writing/SNLI paper/corpus.tex
Revision to coreference para

Existing resources suffer from a subtler issue that impacts even
projects using only human-provided annotations: indeterminacies of
event and entity coreference lead to insurmountable indeterminacy
concerning the correct semantic label (\citealt{de2008finding} $\S4.3$; \citealt{marelli2014sick}). For
instance, the sentence pair \word{A boat sank in the Pacific
  ocean} and \word{A boat sank in an ocean} could reasonably be labeled in
numerous ways depending on how the objects and events are grounded. If
the two boats are assumed to be different, then the sentences are semantically
independent. If the boats and the oceans are assumed to be the same,
then the first sentence entails the second (in the relevant
commonsense way). If the boats are assumed to be the same and 
\word{an ocean} in the second sentence is interpreted with a specific referent 
that is not the Pacific, then the two events are (commonsense) contradictory. This
kind of indeterminacy can be resolved only once the questions of
coreference are resolved.

>>>>

Existing resources suffer from a subtler issue that impacts even
projects using only human-provided annotations: indeterminacies of
event and entity coreference lead to insurmountable indeterminacy
concerning the correct semantic label (\citealt{de2008finding} $\S4.3$; \citealt{marelli2014sick}). 
For instance, the sentence pair \word{A boat sank in the Pacific Ocean} and \word{A boat sank in the Atlantic Ocean} could be labeled as a contradiction if the annotator assumes that the two events under discussion are coreferent, but could also be reasonably labeled as neutral if that assumption is not made. For a similar case with potentially different inutitions, \ii{Ruth Bader Ginsburg was appointed to the US Supreme Court} and \ii{I had a sandwich for lunch today} could be labeled as neutral if the annotator allows that they need not be refer to the same event, but is necessarily a contradiction if the annotator takes coreference to be required. Entity coreference presents a similar kind of uncertainty, as in the pair \word{A tourist visited New York} and \word{A tourist visited the city}. Assuming coreference between \ii{New York} and \ii{the city} justifies labeling the pair as an entailment, but without that assumption \ii{the city} could be taken to refer to a specific unknown city, leaving the pair neutral.

% If
% the two boats are assumed to be different, then the sentences are semantically
% independent. If the boats and the oceans are assumed to be the same,
%then the first sentence entails the second (in the relevant
%commonsense way). If the boats are assumed to be the same and 
%\word{an ocean} in the second sentence is interpreted with a specific referent 
%that is not the Pacific, then the two events are (commonsense) contradictory. This
%kind of indeterminacy can be resolved only once the questions of
%coreference are resolved.
